Future Directions

### 2021-04-04 manuscripts/laplacian_smoothing/arXiv/minimax_optimal_laplacian_smoothing.tex
Found one last typo.
few more changes mostly to Appendix + questions

The Type I error of a test $\phi$ is $\mathbb{E}_0[\phi]$, and if $\mathbb{E}_0[\phi] \leq \alpha$ for a given $\alpha \in (0,1)$ we refer to $\phi$ as a level-$\alpha$ test. The worst-case risk of $\phi$ over $\mc{F}$ is
\begin{equation*}
R_n(\phi, \mc{F}, \epsilon) := \sup\Bigl\{\mathbb{E}_{f_0}[1 - \phi]: f_0 \in \mc{F}, \|f_0\|_{\Leb^2(\mc{X})} > \epsilon\Bigr\},
\end{equation*}
and for a given constant $b \geq 1$, the minimax critical radius $\epsilon(\mc{F})$ is the smallest value of $\epsilon$ such that some level-$\alpha$ test has worst-case risk of at most $1/b$. Formally,
\begin{equation*}
\epsilon(\mc{F}) := \inf\Bigl\{\epsilon > 0: \inf_{\phi} R_n(\phi,\mc{F},\epsilon) \leq 1/b \Bigr\},
\end{equation*} 
where in the above the infimum is over all level-$\alpha$ tests $\phi$, and $\Ebb_{f_0}[\cdot]$ is the expectation operator under the regression function $f_0$.\footnote{Clearly, the minimax critical radius $\epsilon$ depends on $\alpha$ and $b$. However, we adopt the typical convention of treating $\alpha \in (0,1)$ and $b \geq 1$ as small but fixed positive constants; hence they will not affect the testing error rates, and we suppress them notationally.} See \citet{ingster82,ingster87,ingster2012} for a more extended treatment of the minimax paradigm in nonparametric testing.

@@

For a given $0 < \alpha < 1$, define a threshold \smash{$\wh{t}_{\alpha}$} as
\begin{equation*}
\wh{t}_{\alpha} = \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{(\rho \lambda_k + 1)^2} + \frac{1}{n}\sqrt{\frac{2}{\alpha} \sum_{k = 1}^{n} \frac{1}{(\rho \lambda_k + 1)^4}},
\end{equation*}
where we recall $\lambda_k$ is the $k$th smallest eigenvalue of \smash{$L$}. The Laplacian smoothing test is then simply
\begin{equation*}
\wh{\varphi} = \1\bigl\{\wh{T} \leq \wh{t}_{\alpha}\bigr\}.
\end{equation*} 
%(Clearly \smash{$\wh{\varphi}$} depends on $b$, but we suppress this notationally.) 
We show in Appendix~\ref{sec:fixed_graph_error_bounds} that $\wh{f}$ is a level-$\alpha$ test. In the next theorem, we upper bound the worst-case risk $R_n(\wh{\varphi},H^1(\mc{X},M),\epsilon)$ of $\wh{\varphi}$, whenever $\epsilon$ is at least (a constant times) the critical radius given in~\eqref{eqn:sobolev_space_testing_critical_radius}. For this to hold, we will require a tighter range of scalings for the graph radius $r$.
\begin{enumerate}[label=(R\arabic*)]
	\setcounter{enumi}{1}
	\item 
	\label{asmp:ls_kernel_radius_testing}
	For constants $C_0,c_0>0$, the neighborhood graph radius $r$ satisfies
	\begin{equation*}
	C_0\biggl(\frac{\log n}{n}\biggr)^{\frac{1}{d}} \leq r \leq c_0 \wedge M^{\frac{(d - 8)}{8 + 2d}} n^{\frac{d - 20}{32 + 8d}}.
	\end{equation*}
\end{enumerate}
We will also require that the radius of the Sobolev class not be too large. Precisely, we will require $M \leq M_{\max}(d)$, where we define
\begin{equation*}
M_{\max}(d) :=
\begin{cases*}
n^{1/8} & \textrm{$d = 1$} \\
n^{(4 - d)/(4d)} & \textrm{$d \geq 2$}.
\end{cases*}
\end{equation*}

>>>>

The Type I error of a test $\phi$ is $\mathbb{E}_0[\phi]$, and if $\mathbb{E}_0[\phi] \leq \alpha$ for a given $\alpha \in (0,1)$ we refer to $\phi$ as a level-$\alpha$ test. The worst-case risk of $\phi$ over $\mc{F}$ is
\begin{equation*}
R_n(\phi, \mc{F}, \epsilon) := \sup\Bigl\{\mathbb{E}_{f_0}[1 - \phi]: f_0 \in \mc{F}, \|f_0\|_{\Leb^2(\mc{X})} > \epsilon\Bigr\},
\end{equation*}
and for a given constant $b \geq 1$, the minimax critical radius $\epsilon(\mc{F})$ is the smallest value of $\epsilon$ such that some level-$\alpha$ test has worst-case risk of at most $1/b$. Formally,
\begin{equation*}
\epsilon(\mc{F}) := \inf\Bigl\{\epsilon > 0: \inf_{\phi} R_n(\phi,\mc{F},\epsilon) \leq 1/b \Bigr\},
\end{equation*} 
where in the above the infimum is over all level-$\alpha$ tests $\phi$, and $\Ebb_{f_0}[\cdot]$ is the expectation operator under the regression function $f_0$.\footnote{Clearly, the minimax critical radius $\epsilon$ depends on $\alpha$ and $b$. However, we adopt the typical convention of treating $\alpha \in (0,1)$ and $b \geq 1$ as small but fixed positive constants; hence they will not affect the testing error rates, and we suppress them notationally.}

The classical approach to hypothesis testing typically focuses on designing test statistics, and studying their (limiting) distribution in order to ensure control of the Type I error. In many cases the Type II error (or risk in our terminology) is not emphasized, or the risk of the test against fixed or directional alternatives (i.e. alternatives which deviate from the null in a fixed direction) is studied. In contrast, in the minimax paradigm the (uniform or worst-case) risk against a large collection of alternatives is the central focus. See \citet{ingster82,ingster87,ingster2012,ariascastro2018,balakrishnan2019,balakrishnan2018hypothesis} for a more extended treatment of the minimax paradigm in nonparametric testing, and for a discussion of its advantages (and disadvantages) over other approaches to studying hypothesis tests.

@@

For a given $0 < \alpha < 1$, define a threshold \smash{$\wh{t}_{\alpha}$} as
\begin{equation*}
\wh{t}_{\alpha} = \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{(\rho \lambda_k + 1)^2} + \frac{1}{n}\sqrt{\frac{2}{\alpha} \sum_{k = 1}^{n} \frac{1}{(\rho \lambda_k + 1)^4}},
\end{equation*}
where we recall $\lambda_k$ is the $k$th smallest eigenvalue of \smash{$L$}. The Laplacian smoothing test is then simply
\begin{equation*}
\wh{\varphi} = \1\bigl\{\wh{T} > \wh{t}_{\alpha}\bigr\}.
\end{equation*} 
%(Clearly \smash{$\wh{\varphi}$} depends on $b$, but we suppress this notationally.) 
We show in Appendix~\ref{sec:fixed_graph_error_bounds} that $\wh{f}$ is a level-$\alpha$ test. In the next theorem, we upper bound the worst-case risk $R_n(\wh{\varphi},H^1(\mc{X},M),\epsilon)$ of $\wh{\varphi}$, whenever $\epsilon$ is at least (a constant times) the critical radius given in~\eqref{eqn:sobolev_space_testing_critical_radius}. For this to hold, we will require a tighter range of scalings for the graph radius $r$.
\begin{enumerate}[label=(R\arabic*)]
	\setcounter{enumi}{1}
	\item 
	\label{asmp:ls_kernel_radius_testing}
	For constants $C_0,c_0>0$, the neighborhood graph radius $r$ satisfies
	\begin{equation*}
	C_0\biggl(\frac{\log n}{n}\biggr)^{\frac{1}{d}} \leq r \leq c_0 \wedge M^{\frac{(d - 8)}{8 + 2d}} n^{\frac{d - 20}{32 + 8d}}.
	\end{equation*}
\end{enumerate}
We will also require that the radius of the Sobolev class not be too large. Precisely, we will require $M \leq M_{\max}(d)$, where we define
\begin{equation*}
M_{\max}(d) :=
\begin{cases*}
n^{1/8} & \textrm{$d = 1$} \\
n^{(4 - d)/(4d)} & \textrm{$d \geq 2$}.
\end{cases*}
\end{equation*}
